# Reproducible Research: Peer Assessment 1
==========================================

## Introduction

This document describes the proedure to accomplish the above mentioned assignment. It assumes that **Activity Monitoring Dataset** file *activity.csv* is in the same folder as this document.  

## Data Description

Describe the data set here.  

## Assignment

Some description of the assignment

## Loading various packages

```{r}
library(plyr)
library(lattice)
```


## Loading and preprocessing the data


```{r}
df = read.csv("activity.csv", stringsAsFactor=F)
str(df)
```

The *date* field is converted to date datatype.  

A new filed **period** is added with a format of **HHMM** using *interval* field.  

```{r}
df$date = as.Date(df$date, "%Y-%m-%d")
df$period = sprintf("%04d", df$interval)
str(df)
```

## What is mean total number of steps taken per day?
```{r}
dfDaily = ddply(df, .(date), summarise, dailySteps=sum(steps, na.rm=T))
```

```{r fig.width=7, fig.height=6}
hist(dfDaily$dailySteps, breaks=25)
```

```{r}
# histogram(dfDaily$dailySteps, breaks=25, main="Histogram of Daily Steps Taken", xlab="Daily Total Steps", ylab="Frequency")
```

## What is the average daily activity pattern?


## Imputing missing values


## Are there differences in activity patterns between weekdays and week


